### 2023-10-17 Appendices/appendixA.tex
Return to line
Added figure to pdf

\begin{equation}\label{eq:hSigmoid}
  \sigma (x) =
  \begin{cases}
    0, \hfill x< -2.5\\
    \frac{x}{5}+\frac{1}{2}, \hspace{0.2cm} 2.5>x>-2.5\\
    1, \hfill x> 2.5\\
  \end{cases}
\end{equation}
\begin{equation}\label{eq:hTanh}
  tanh(x) =
  \begin{cases}
    -1, \hfill x<-1\\
    x, \hspace{0.2cm} 1>x>-1\\
    1, \hfill x>1\\
  \end{cases}
\end{equation}

>>>>

\begin{equation}\label{eq:hSigmoid}
  \sigma (x) =
  \begin{cases}
    0, \hfill x< -2.5\\
    \frac{x}{5}+\frac{1}{2}, \hspace{0.2cm} 2.5>x>-2.5\\
    1, \hfill x> 2.5\\
  \end{cases}
\end{equation}

\begin{equation}\label{eq:hTanh}
  tanh(x) =
  \begin{cases}
    -1, \hfill x<-1\\
    x, \hspace{0.2cm} 1>x>-1\\
    1, \hfill x>1\\
  \end{cases}
\end{equation}

Some versions of the hard sigmoid are a bit different from \cref{eq:hSigmoid}, the slope depends on the library used \cite{hSigmoid1}.

\begin{figure}[H]
  \centering
  \includesvg[width=\textwidth]{activation/hardFunc}
  \caption{Hard sigmoid and hard \acs{tanh} with their original function}
  \label{graph:hardFunc}
\end{figure}

A visual representation helps seeing how close those functions are, \cref{graph:hardFunc} displays the two together with the function they are modeled after.
